### 2021-12-07 input/figundoproblem.tex
meow
reworked order of things

\begin{figure*}
  \newcommand{\SCALE}{0.9}

  \newcommand{\LEFT}{\triangleleft}
  \newcommand{\RIGHT}{\triangleright}

  \begin{center}
    \subfloat[Part A][\label{fig:undoproblemA}$a$ and $c$ become sources.
      $w_{ab} = 2$; $w_{bc} = 1$.]{\input{input/figundoproblemA.tex}}
    \hspace{0pt}
    \subfloat[Part B][\label{fig:undoproblemB}($c$ deletes its partition but $a$ does not.
      $b$ delivers and forwards $\alpha_a$.]
             {\input{input/figundoproblemB.tex}}
    \hspace{0pt}
    \subfloat[Part C][\label{fig:undoproblemC}$b$ delivers and forwards $\alpha_c$.]
             {\input{input/figundoproblemC.tex}}
    \hspace{0pt}
    \subfloat[Part D][\label{fig:undoproblemD}(both) $b$ delivers and forwards $\delta_c$.]
             {\input{input/figundoproblemD.tex}}
  \end{center}
  \caption{\label{fig:undoproblem}From $c$'s perspective, this
    scenario and Figure~\ref{fig:problem} are similar. Even when $a$
    did not delete its partition, $c$ must acknowledge $P_a$'s
    \emph{possible} deletion and propagate it.}
\end{figure*}

>>>>

\begin{figure*}
  \newcommand{\SCALE}{0.9}
  \newcommand{\LEFT}{\triangleleft}
  \newcommand{\RIGHT}{\triangleright}
  \begin{center}
    \subfloat[Part A][\label{fig:undoproblemA}$a$ and $c$ become sources.
      $w_{ab} = 2$; $w_{bc} = 1$.]{\input{input/figundoproblemA.tex}}
    \hspace{0pt}
    \subfloat[Part B][\label{fig:undoproblemB}$c$ deletes its partition but $a$ does not.
      $b$ delivers and forwards $\alpha_a$.]
             {\input{input/figundoproblemB.tex}}
    \hspace{0pt}
    \subfloat[Part C][\label{fig:undoproblemC}$b$ delivers and forwards $\alpha_c$.]
             {\input{input/figundoproblemC.tex}}
    \hspace{0pt}
    \subfloat[Part D][\label{fig:undoproblemD}$b$ delivers and forwards $\delta_c$.]
             {\input{input/figundoproblemD.tex}}
  \end{center}
  \caption{\label{fig:undoproblem}From $c$'s perspective, this
    scenario and Figure~\ref{fig:problem} are similar. Even when $a$
    did not delete its partition, $c$ must acknowledge $P_a$'s
    \emph{possible} deletion and propagate it.}
\end{figure*}

### 2021-12-07 input/proposal.tex
reworked order of things

A naive implementation resembles echos in acoustics:
\underline{d}elete notifications $\delta$ propagate as long as
receivers' current partition is the targeted one, and when delete
notifications reach the bordering \processes of the deleted partition,
it triggers a competition -- or an echo -- that goes backward to fill
the gap left open by removals.  For example, in Figure~\ref{fig:del},
two partitions initially exist: $P_a$ and $P_d$ that respectively
include $\{a\}$, and $\{b, c, d\}$. In Figure~\ref{fig:delA}, $a$
deletes its partition. It notifies all neighboring \processes~--~here
only $b$~-- that may belong to its partition using \NAMEB. Upon
receipt, $b$ discards the delete notification $\delta_a$ since
$\delta_a$ does not target the former's partition $P_d$. \Process~$b$
sends its own best partition $\alpha_d^3$ that may be the best for
$a$. Eventually, every \process belongs to Partition $P_d$. In this
scenario, they reach consistent partitioning.

%% Unfortunately, depending on receipt order of messages, \processes may
%% converge to

Delete operations add a new notion of order between events, and most
importantly between message deliveries. Delete operations implicitly
state that all preceding events become obsolete, and that all messages
originating from these preceding events convey stale control
information.

@@

@@

\TODO{The naive implementation described above is $\textup{FB}^+
  \wedge FS$. And it does  not work.}

>>>>

Delete operations bring a new notion of order between events, and most
importantly between message deliveries. When a \process $s$ performs a
\texttt{Del} operation, this implicitly states that all its preceding
\texttt{Add} operations become obsolete. As consequence, their results
-- scoped broadcast in the form of \texttt{\underline{A}dd}
notifications $\alpha_s$ -- should be canceled by the corresponding
\texttt{\underline{D}el} notifications $\delta_s$.

@@

A naive implementation based on scoped broadcast as stated in
Definition~\ref{def:scoped} resembles echos in acoustics: staleness
notifications propagate as long as receivers' current partition is the
targeted one, and when staleness notifications reach the bordering
\processes of the deleted partition, it triggers a competition -- or
an echo -- that goes backward to fill the gap left open by removals.

@@

Figure~\ref{fig:del} illustrates the behavior of this intuitive
implementation.  Two partitions initially exist: $P_a$ and $P_d$ that
respectively include $\{a\}$, and $\{b, c, d\}$. In
Figure~\ref{fig:delA}, $a$ deletes its partition. It notifies all
neighboring \processes~--~here only $b$~-- that may belong to its
partition. Upon receipt, $b$ discards the delete notification
$\delta_a$ since $\delta_a$ does not target the former's partition
$P_d$. \Process~$b$ sends its own best partition $\alpha_d^3$ that may
be the best for $a$. Eventually, every \process belongs to Partition
$P_d$. In this scenario, they reach consistent
partitioning. Unfortunately, this protocol does not ensure consistent
partitioning in every scenario.

% \TODO{The naive implementation described above is $\textup{FB}^+
%  \wedge FS$. And it does  not work.}
